A Fully Decentralized Infrastructure for Subscription-based IoT Data Trading

### 2020-07-15 paper.tex
Use "Accel" for Tangle-accelerator

Transferring MAM operations to brokers while ensuring the profit and privacy of providers through blind signatures can effectively solve performance problems and lower the threshold to participate in such framework. Brokers can be PCs or powerful machines that runs Ethereum client and Tangle-accelerator, where Ethereum client is used to interact with Ethereum and Tangle-accelerator provides PoW acceleration and MAM delegation. Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with 500 bytes payload with local PoW on RPi, remote Pow on Tangle-accelerator and E2EE on RPi. However, MAM operations are fairly time-consuming that improving the performance of MAM is an essential issue that needs to be done for the next step.

@@

\subsubsection{Experiment}
PoW, sending to IOTA full node and creating channel these three steps take most of the time to broadcast a MAM message. Applying remote PoW greatly reduces the elapsed time. To improve MAM into a reliable solution for low-level devices, channel creation is the next primary barrier should be removed. With employing delegated MAM and E2EE, MAM channel creation would be delegated to Tangle-accelerator which dramatically enhances the efficiency and makes MAM available for low-level devices. What follows is the performance comparison between MAM and delegated MAM for different payload sizes. Elapsed time for internet communication and PoW are not included, because the processes after sending messages to Tangle-accelerator are the common steps. Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly. In addition, MAM channel creation and E2EE asymmetric key pair generation are not included, too, because the two operations would seldom be executed. In the E2EE protocol, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and Curve P-256 for ECDSA, respectively.

@@

The steps counted in delegated MAM (E2EE) benchmark including:
\begin{enumerate}
	\item Generate symmetric key for encryption
	\item Hash input payload
	\item Encrypt input payload
	\item Transmit final message to tangle-accelerator
\end{enumerate}

@@

Table~\ref{tab:mam_vs_e2ee} is the experiment result of the two methods. Eq.~\ref{lin_mam},~\ref{lin_e2ee} are the linear equations for the experiment data of MAM and E2EE respectively. The result reveals elapsed time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for resource-constrained systems to send authenticated streaming data. The slope of the result of E2EE is much more flat than the result of MAM which ensures E2EE can consistently perform in an acceptable time range. Under our design which delegate MAM operations with Tangle-accelerator and the presented E2EE protocol, data provider can include resource-constrained hardware into the data subscription economy. E2EE protocol promises tamperless data transmission, and only authorized subscribers can read the encrypted information.

>>>>

Transferring MAM operations to brokers while ensuring the profit and privacy of providers through blind signatures can effectively solve performance problems and lower the threshold to participate in such framework. Brokers can be PCs or powerful machines that runs Ethereum client and Accel, where Ethereum client is used to interact with Ethereum, and Accel provides PoW acceleration and MAM delegation. Fig.~\ref{fig:rpi3_pow} shows the time cost of sending a MAM message with 500 bytes payload with local PoW on RPi, remote PoW on Accel and E2EE on RPi. However, MAM operations are fairly time-consuming that improving the performance of MAM is an essential issue that needs to be done for the next step.

@@

\subsubsection{Experiment}
PoW, sending to IOTA full node and creating channel these three steps take most of the time to broadcast a MAM message. Applying remote PoW greatly reduces the elapsed time. To improve MAM into a reliable solution for low-level devices, channel creation is the next primary barrier should be removed. With employing delegated MAM and E2EE, MAM channel creation would be delegated to Accel which dramatically enhances the efficiency and makes MAM available for low-level devices. What follows is the performance comparison between MAM and delegated MAM for different payload sizes. Elapsed time for internet communication and PoW are not included, because the processes after sending messages to Accel are the common steps. Excluding the common steps allows us to compare the performance between MAM and delegated MAM more clearly. In addition, MAM channel creation and E2EE asymmetric key pair generation are not included, too, because the two operations would seldom be executed. In the E2EE protocol, we choose SHA-256 for HMAC, AES-CBC for symmetric encryption and Curve P-256 for ECDSA, respectively.

@@

The steps counted in delegated MAM (E2EE) benchmark including:
\begin{enumerate}
	\item Generate symmetric key for encryption
	\item Hash input payload
	\item Encrypt input payload
	\item Transmit final message to Accel
\end{enumerate}

@@

Table~\ref{tab:mam_vs_e2ee} is the experiment result of the two methods. Eq.~\ref{lin_mam},~\ref{lin_e2ee} are the linear equations for the experiment data of MAM and E2EE respectively. The result reveals elapsed time of E2EE is obviously less than elapsing time of MAM which shows the E2EE process presented in the paper is a much more appropriate solution for resource-constrained systems to send authenticated streaming data. The slope of the result of E2EE is much more flat than the result of MAM which ensures E2EE can consistently perform in an acceptable time range. Under our design which delegate MAM operations with Accel and the presented E2EE protocol, data provider can include resource-constrained hardware into the data subscription economy. E2EE protocol promises tamperless data transmission, and only authorized subscribers can read the encrypted information.
